Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms

### 2018-04-16 paper/paper.tex
More abstract

\begin{abstract}
    Modern subgraph isomorphism solvers use degree-based value-ordering heuristics to direct
    backtracking search. We show that discrepancy-based searches are too expensive to be effective
    in offsetting heuristic mistakes in this situation.  We then demonstrate that a random heuristic
    with restarts beats conventional search with the best-known tailored heuristic. This motivates
    the introduction of a slightly-random heuristic with similar behaviour to the tailored
    heuristic: when combined with restarts, this new search strategy is over a hundred times more
    effective on satisfiable instances, and does not affect performance on unsatisfiable instances.
    Finally, we show that this strategy also improves two maximum common induced subgraph
    algorithms.
\end{abstract}

>>>>

\begin{abstract}
    Modern subgraph isomorphism solvers use degree-based value-ordering heuristics to direct
    backtracking search. This kind of search makes a heavy commitment to the first branching choice,
    which is often incorrect. We evaluate discrepancy-based searches as an alternative, but find
    them too expensive to be effective in this situation, even on satisfiable instances. We then
    demonstrate that a random value-ordering heuristic with restarts beats conventional search with
    the best-known tailored heuristic. This motivates the introduction of a slightly-random
    heuristic with similar behaviour to the tailored heuristic: when combined with restarts and
    nogood recording, this new search strategy is over a hundred times more effective on satisfiable
    instances, and does not affect performance on unsatisfiable instances.  Finally, we show that
    this strategy also improves two maximum common induced subgraph algorithms.
\end{abstract}
